---
title: "CreesysOverview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CreesysOverview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE, 
  message = FALSE
)
```

## Importing Data with `gfsR`

The `gfsR` package provides an import function that allows users to import data to their R environment directly from a FishNet2 DATA.ZIP file format. The `import_fn_creel` function returns the necessary design and data tables as dataframes within a list. The following example provides a brief overview of how to retrieve data from this format.

```{r gfsR, eval=FALSE}
library(gfsR)
creel_zip <- "Documents/SC00_XXX/DATA.ZIP"
creel_data <- import_fn_creel(creel_zip)
```

## Using Preloaded Example Data

```{r setup}
library(creesysr)
library(dplyr)
library(hms)
library(knitr)
library(kableExtra)
library(htmltools)
data("SC00")
names(SC00)
SC00$FN011
```

## Generating the Results
```{r data-analysis}
SC00_analysis <- generate_FR713_714_tables(SC00$FN011, SC00$FN022, SC00$FN023, SC00$FN024,
                                           SC00$FN025, SC00$FN026, SC00$FN028, SC00$FN111, 
                                           SC00$FN112, SC00$FN121, SC00$FN123)
```

## Display as an FN2 Output
```{r fn2display, render="as.is"}
library(htmltools)
library(kableExtra)
html_content <- tagList(
    HTML(SC00_analysis[[1]]),
    HTML(SC00_analysis[[2]])
  )
html_content
```

